\bf Climbing

### 2021-07-27 manuscript/Rmd/draft.tex
Update Rmd

Copy from Rnw + Edit

@@

\hypertarget{why-product-of-ranks-instead-of-sum}{%
\subsubsection{Why product of ranks instead of
sum}\label{why-product-of-ranks-instead-of-sum}}

@@

We collected data on major climbing competitions from 2018 to 2020,
including the 2020 Continental Championships of Europe, Africa, Oceania,
Pan-America; 2019 and 2018 World Championships; 2018 Asian Games; and
2018 Asian Games. We are interested in looking at the relationships
between the ranks of the individual events and the final standings, and
we computed Kendall's Tau (Kendall Rank Correlation Coefficient).

Figure 3 is a scatterplot and correlation matrix between the ranks for
the 2018 Youth Olympics Women's Qualification.

It is evidently clear that there is a strong and positive correlation
between the ranks of bouldering and lead climbing, and as a results, the
standings of these two events are highly correlated with the final
rankings. On the other hand, the relationship is not as strong for speed
climbing. Thus, speed climbers are facing a huge disadvantage in this
scoring system, compared to those that are specialized in the other two
concentrations.

@@

>>>>

(Copy from Rnw + Edit)

\hypertarget{sport-climbing}{%
\subsection{Sport Climbing}\label{sport-climbing}}

\hypertarget{other-scoring-systems}{%
\subsection{Other Scoring Systems}\label{other-scoring-systems}}

@@

\hypertarget{sum-of-ranks-instead-of-product}{%
\subsubsection{Sum of ranks instead of
product}\label{sum-of-ranks-instead-of-product}}

@@

For our analysis on the relationship between the rankings of the events
and the final result, we used data from the 2018 Youth Olympics Women's
Qualification. Figure 3 is a scatterplot and correlation matrix between
the ranks of the individual events and the final standings, with
Kendall's Tau (Kendall Rank Correlation Coefficient) as our measure of
ordinal association between the quantities. It is evidently clear that
there is a strong and positive correlation between the ranks of
bouldering and lead climbing, and as a results, the standings of these
two events are highly correlated with the final rankings. On the other
hand, the correlation with the final rank is not as strong for speed
climbing. Thus, speed climbers are facing a huge disadvantage in this
scoring system, compared to those that are specialized in the other two
concentrations.

This trend also holds for most of the past competitions.

@@

A single climber excluded changes things drastically, especially order
of medalists.

The cases where someone behind you drops out and your ranking changes.

Example from 2018 youth, women's final dropping ranks 3 and 5 change the
medalist order

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{Original rankings and rankings after each rank is dropped}
\end{figure}
